\begin{longtable}{p{.33\textwidth}p{.67\textwidth}}
\textbf{Bio}      & Participant came to Münster from Iran three years ago \\
\textbf{Age}      & 28                                                    \\
\textbf{Gender}   & M                                                     \\
\textbf{Date}     & Nov. 21, 2018                                         \\
\textbf{Duration} & 0:58:37                                               \\
\end{longtable}

\renewcommand{\arraystretch}{1.5}

\begin{longtable}{p{.33\textwidth}p{.67\textwidth}}
\textbf{Question}                                                                                                                                               & \textbf{Answer}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                 \\
{[}00:00:34{]} Please introduce yourself and describe your life in Münster. What do you do on a normal day?                                                     & Participant met many nice people after arriving in Münster. He meets up with his friends almost every weekend and goes out. He used to work for a German company but registered for disability one month ago because he has to have an operation. At the same time, he attends a C1 level German class.                                                                                                                                                                                                                                                                                         \\
                                                                                                                                                                & On a normal day, he used to work during the day and go to German class at night. He now doesn't work and does a lot of homework. On the weekends he goes out. He lives in an apartment by himself in a suburb of Münster and always rides his bike (hasn't bought a bus ticket for two years).                                                                                                                                                                                                                                                                                                  \\
                                                                                                                                                                & He lived for one month in another city in Germany before he came to Münster. He feels particularly good in Münster because the people who live here are all in his generation, fresh and young.                                                                                                                                                                                                                                                                                                                                                                                                 \\
{[}00:06:31{]} Please describe your contact with people outside of your extended family in Münster.                                                             & Participant has contact with his family still but is totally alone in Germany. He has friends with whom he goes out on the weekends, drinking, going to bars. He also has friends with whom he just learns languages.                                                                                                                                                                                                                                                                                                                                                                           \\
                                                                                                                                                                & Participant has one friend who was a teacher at his language school (although not his teacher) and comes from an Asian country. Participant teaches him Persian in exchange for little lessons in his native language. He met him when the teacher greeted him in Persian (because a classmate found out the teacher was learning Persian) and they by chance rode the bus together. They got connected over Facebook, started doing a language tandem, have stayed in touch for a long time.                                                                                                    \\
                                                                                                                                                                & Participant fled Iran with 3 others. One disappeared on the border with Austria but turned up later in Hamburg. The two others were placed in Bielefeld when he was placed in Münster. So he came to Münster all alone and was placed in a house with people of many different nationalities. This was difficult because he couldn't communicate well with his roommates. He can only speak a little English and Arabic. So he decided he had to learn German.                                                                                                                                \\
                                                                                                                                                                & They had social workers in the accommodation facility. He had practical skills and time (he was only doing a German course) and wanted to meet people and learn about German culture. So he went to the accommodation facility where they were renovating and he volunteered to help. He learned the German word ``Kollege'' from this experience, for example.                                                                                                                                                                                                                                     \\
                                                                                                                                                                & The head of maintenance ``Joe'' saw him helping for two weeks and offered to give him a ``one Euro job,'' a position with a very low wage, which allowed him to keep receiving the refugee money. He worked there for 6 or 7 months and met new people. When he had trouble with German homework, people there helped him.                                                                                                                                                                                                                                                                          \\
                                                                                                                                                                & He helped ``Joe'' (who is about the same age) with whatever he needed, and ``Joe'' invited him to concerts, introducing him to Western culture. He was always with ``Joe'' and met many people through ``Joe'' until ``Joe'' moved away. He met his driving instructor ``John'' through ``Joe'' when they were out drinking together one time. ``John'' told him to come and convert his driver's license at his place. Participant used guessing tricks and logical deduction to pass the written test, since he didn't understand the questions. Failed the practical test two times because of language issues before passing on the third try. \\
{[}00:10:52{]} Probe: How often do you have contact with such people? When was the last time?                                                                   & He goes out almost every weekend or every other weekend.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        \\
{[}00:25:09{]} Probe: What motivates you to do this?                                                                                                            & Learning the language was the most important goal in his life.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \\
                                                                                                                                                                & Second was to get to know the culture. Curiosity about food, traditions, etc.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                   \\
                                                                                                                                                                & Also to be able to ask questions, and sometimes get the right answer, to improve his life.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      \\
{[}00:27:02{]} Probe: How do you feel when you make contact with people outside of your extended family?                                                        & He feels very excited when he makes new contacts and can talk about his life with them. He feels like a kid. He is always learning new things, it's like reading an exciting novel. He doesn't feel how the time is going by. For other people, everything is routine, but for forced migrants, everything is new. For example, he had never done an interview or had contact with an American before this interview.                                                                                                                                                                           \\
{[}00:29:17{]} Probe: What are your main methods for making contact with people here?                                                                           & For every contact he has a goal. He asks himself, why should I stay in contact with this person? What are the pros and cons? Every friend is different. For friends who come from other countries, he can help them. He learns languages from other friends. ``Joe'' is a good man, and helped him practice his German. He also could meet many people through ``Joe''.                                                                                                                                                                                                                             \\
{[}00:32:00{]} Probe: Which of these should be supported by a system?                                                                                           & Apps have pros and cons. Through an app, you can't tell what thoughts a person has. Through personal contact you can understand people better, but through an app you can save time. You can break off contacts that aren't going well more easily. You can make contact with people who are far away. Language tandems could be supported by an app, so that you could talk with someone in other countries.                                                                                                                                                                                   \\
{[}00:37:14{]} Probe: Which tools are necessary to make social contact as a newcomer? Which tools are missing? What tools do you wish existed?                  & Bars and beer are his tool. He wants to try living without a cellphone though. Using Facebook too much actually made him sad, reading news in Persian.                                                                                                                                                                                                                                                                                                                                                                                                                                          \\
                                                                                                                                                                & On the other hand, all of his friends use WhatsApp and Facebook, so they are necessary in order to stay in contact. He can't think of any tools that are missing.                                                                                                                                                                                                                                                                                                                                                                                                                               \\
{[}00:42:14{]} What is necessary for successfully making contacts here?                                                                                         & The ability to act nice, to make a nice impression. To think about how to get along with people. He always tries to remain polite and kind.                                                                                                                                                                                                                                                                                                                                                                                                                                                  \\
{[}00:43:25{]} Probe: Do you need any specific knowledge to successfully make contacts here? Are you lacking any knowledge?                                     & He has to act cool and relaxed, even if he is tired or upset. Even with someone who is his opponent, he has to act modest (bescheiden). That's something that works well in Germany: people even respect their opponents and are not arrogant.                                                                                                                                                                                                                                                                                                                                                  \\
{[}00:45:26{]} When you want to meet up with someone in Münster, how do you proceed?                                                                            & He invites them for a coffee or cooks some Persian food at home and invites them to his place. On the second meeting he takes something with him, like gum or a chocolate, something! He always has gum in his bag and he often offers it to start a conversation.                                                                                                                                                                                                                                                                                                                              \\
                                                                                                                                                                & Also makes small talk about the weather when he's waiting in a doctor's office or something because he knows everyone is bored and might want to talk. He has made friends this way at the language school. But even if he doesn't make friends, it makes the moment better. He isn't trying to make long-term contacts every time.                                                                                                                                                                                                                                                               \\
                                                                                                                                                                & He sees his neighbors very seldom. He is considering inviting them to a meal at his place though, because he thinks neighborly contact is important.                                                                                                                                                                                                                                                                                                                                                                                                                                            \\
{[}00:51:11{]} Probe: Can things go wrong? If so, how do you become aware of that?                                                                              & When one always talks about one's self. Then people don't answer your messages anymore and then they don't meet you anymore. Also when you are too stingy. It helps friendship when you pay for each other from time to time.                                                                                                                                                                                                                                                                                                                                                                   \\
{[}00:52:28{]} Probe: Are there any safety-critical aspects?                                                                                                    & When people make fun of him, it bothers him. Even if it isn't really serious, so he tries to just avoid it.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     \\
{[}00:54:30{]} Based on this conversation, do you have any ideas for new ways people in Münster can come together to address the social isolation of newcomers? & One should found clubs for different subjects that don't cost very much (medicine, technical things, etc.). Clubs just for newcomers. And there should be possibilities in every language. It shouldn't be a club for refugees, but for all newcomers.                                                                                                                                                                                                                                                                                                                                          \\
\end{longtable}

\renewcommand{\arraystretch}{1}
