\chapter{Context Interviews}
\label{app:interviews}

\section{Interview Script}
\label{app:interview-script}

\subsection*{Preparation}

\begin{itemize}
    \item Put signed consent form, recorder, notebook, and two pens on the table
    \item Welcome and thank participant
    \item Explain what we are studying and why
    \begin{itemize}
        \item Illustrate technical possibilities of a location-based service
    \end{itemize}
    \item Explain focus on tasks, not systems
    \item Explain that interviewer won’t be judging, there is no wrong answer
    \item Assure confidentiality and that interviewee can check facts
    \begin{itemize}
        \item Will record audio to remember what is said, but won’t share it with anyone
        \item May include unidentifiable quotes in final work
    \end{itemize}
    \item Explain consent form
    \item Ask participant to read and sign
    \item Ask if there are any questions
    \item Explain that recording will start now and interviewer will begin by asking for name, age, and verbal consent
\end{itemize}

\subsection*{Interview}

\begin{itemize}    \item Start recorder
    \item Request consent statement
    \begin{itemize}
        \item Please state your name and age.
        \item Could you please say again, do you agree to have me record this interview?
    \end{itemize}
    \item Perform interview
    \item Stop recorder
\end{itemize}

\subsection*{Conclusion}

\begin{itemize}
    \item Thank participant again
    \item Ask if they are interested in the results, and if so, note their preferred contact information
    \item Ask if they want to test the app in the second part of the study, and if so, make a note
    \item Ask if they know anyone else who might be interested in participating in the study
\end{itemize}


\section{Interview Questions (Forced Migrants)}
\label{app:interview-questions-fm}

\begin{enumerate}
    \item \textbf{Opening:} Please introduce yourself and describe your life in Münster. What do you do on a normal day?\par\par

    \item \textbf{Introduction by the researcher:} Describe the issue of social isolation and its opposite: social contact

    \item \textbf{Involvement:} Please describe your contact with people outside of your extended family in Münster.

    \begin{itemize}
        \item Probe: How often do you have contact with such people? When was the last time?
        \item Probe: Where do you have contact with people outside of your extended family?
        \item Probe: What motivates you to do this?
        \item Probe: How do you feel when you make contact with people outside of your extended family?
        \item Probe: What are your main methods for making contact with people here?
        \item Probe: Which of these should be supported by a system?
        \item Probe: Which tools are necessary to make social contact as a newcomer? Which tools are missing? What tools do you wish existed?
    \end{itemize}

    \item \textbf{Prerequisites:} What is necessary for successfully making contacts here?

    \begin{itemize}
        \item Probe: Do you need any specific knowledge? Are you lacking any knowledge?
        \item Probe: Which skills do you need? Are you lacking any skills?
        \item Probe: What does making contacts require of you (physically and mentally)?
    \end{itemize}

    \item \textbf{Execution:} When you want to meet someone here, how do you proceed?

    \begin{itemize}
        \item Probe: What are the steps you take when making first contact?
        \item Probe: Can things go wrong? If so, how do you become aware of that?
        \item Probe: Are there any safety-critical aspects?
    \end{itemize}

    \item \textbf{Closing:} Based on this conversation, do you have any ideas for new ways people in Münster can come together to address the social isolation of newcomers?

    \begin{itemize}
        \item Probe: What could be better here?
        \item Probe: What already works well?
    \end{itemize}
\end{enumerate}





\section{Interview Questions (Freecyclers)}
\label{app:interview-questions-freecyclers}

\begin{enumerate}
    \item \textbf{Opening:} Please introduce yourself and describe your life in Münster. What do you do on a normal day?\par\par
    
    \item \textbf{Introduction by the researcher:} Explain the concept of freecycling and how it relates to the user’s platform of choice.

    \item \textbf{Involvement:} Please describe your experience with freecycling.

    \begin{itemize}
        \item Probe: How often do you freecycle? When was the last time you freecycled?
        \item Probe: Where do you freecycle?
        \item Probe: What motivates you to freecycle?
        \item Probe: How do you feel when you freecycle?
    \end{itemize}

    \item \textbf{Execution:} When you want to freecycle successfully, what do you have to do?

    \begin{itemize}
        \item Probe: What are the specific steps you take?
        \item Probe: Which of these steps should be supported by a system?
        \item Probe: Can you make mistakes? If so, how do you become aware of them?
    \end{itemize}

    \item \textbf{Prerequisites:} What are the necessary qualifications for freecycling?

    \begin{itemize}
        \item Probe: Do you need specific knowledge? Are you lacking any knowledge?
        \item Probe: Which skills do you need? Are you lacking any skills?
        \item Probe: What do the steps demand of you (physically and mentally)?
    \end{itemize}

    \item \textbf{Closing:} Based on this conversation, do you have any ideas for ways to improve existing freecycling systems in Münster?

    \begin{itemize}
        \item Probe: Which tools are necessary?
        \item Probe: Which are missing?
        \item Probe: Which are desired in addition?
    \end{itemize}
\end{enumerate}


\section{Interview Questions (Freecycling Moderators)}
\label{app:interview-questions-moderators}

\begin{enumerate}
    \item \textbf{Opening:} Please introduce yourself and describe your life in Münster. What do you do on a normal day?\par\par
    
    \item \textbf{Introduction by the researcher:} Explain the concept of freecycling and how it relates to the moderator’s system.

    \item \textbf{Involvement:} What do you do as a moderator of a freecycling system?

    \begin{itemize}
        \item Probe: How often do you actively moderate?
        \item Probe: Where do you do this?
        \item Probe: What motivates you to do this?
        \item Probe: How do you feel when you do this?
    \end{itemize}

    \item \textbf{Execution:} What tasks are involved in moderating?

    \begin{itemize}
        \item Probe: What are the specific steps you take [tasks]?
        \item Probe: Which of these tasks should be supported by a system?
        \item Probe: Can you make mistakes? If so, how do you become aware of them?
    \end{itemize}

    \item \textbf{Prerequisites:} What are the necessary qualifications for moderating?

    \begin{itemize}
        \item Probe: Do you need specific knowledge? Are you lacking any knowledge?
        \item Probe: Which skills do you need? Are you lacking any skills?
        \item Probe: What do the tasks demand of you (physically and mentally)?
    \end{itemize}

    \item \textbf{Closing:} Based on this conversation, do you have any ideas for ways to improve existing freecycling systems in Münster?

    \begin{itemize}
        \item Probe: Which tools are necessary?
        \item Probe: Which are missing?
        \item Probe: Which are desired in addition?
    \end{itemize}
\end{enumerate}
